\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-26 paper/ms.tex
all numbers to be consistent with f_CZ=0.02

The accretion scenario can naturally explain the anomalously high
surface \elem{Li} abundance in \bizarreone.
Because \elem{Li} is strongly depleted in old sun-like stars, yet
present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
late-time accretion of rocky planetary material will significantly
replenish the lithium in the star's surface.
For the present-day Sun, the accretion of $15~\mearth$ of bulk Earth-like
material would result in $\Delta\elemH{Li} \approx 1.6$~dex
(see inset of \figname~\ref{fig:deltaxh_tcrank}).
Incidentally, the \bizarreone-\sunanalog\ system has an age (informed by
stellar parameters) very close to the Sun ($\sim 4$~Gyr).
Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
to be ordinary, the accretion of $20$~\mearth\ by \bizarreone\ is consistent with a $1.6$~dex
enhancement in \elem{Li} abundance.
This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep.)
approximately $1.65$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
Furthermore, this implies that the accretion event should have happened
recently within the \elem{Li} depletion time ($\lesssim 1$~Gyr).

>>>>

The accretion scenario can naturally explain the anomalously high
surface \elem{Li} abundance in \bizarreone.
Because \elem{Li} is strongly depleted in old sun-like stars, yet
present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
late-time accretion of rocky planetary material will significantly
replenish the lithium in the star's surface.
For the present-day Sun, the accretion of $15~\mearth$ of bulk Earth-like
material would result in $\Delta\elemH{Li} \approx 1.6$~dex
(see inset of \figname~\ref{fig:deltaxh_tcrank}).
Incidentally, the \bizarreone-\sunanalog\ system has an age (informed by
stellar parameters) very close to the Sun ($\sim 4$~Gyr).
Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
to be ordinary, the accretion of $15$~\mearth\ by \bizarreone\ is consistent with a $1.65$~dex
enhancement in \elem{Li} abundance.
This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep.)
approximately $1.7$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
Furthermore, this implies that the accretion event should have happened
recently within the \elem{Li} depletion time ($\lesssim 1$~Gyr).
